### 2020-04-21 final_report/data.tex
add tbr vs. feature plot
use chemical package in H2O in figure description
LaTeXify autoencoder plots

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{rllll}
		\toprule
		\#	& Sample count & Job division & Run time (incl. waiting) & Description \\
		\midrule
		0 & \num{100000} & $\num{100}\times\num{1000}$ & 2~days, 23~hours &
		Testing run using older MC TBR version.\\
		1 & \num{500000} & $\num{500}\times\num{1000}$ & 13~days, 20~hours &
		Fully uniform sampling in the entire domain.\\
		2 & \num{400000} & $\num{400}\times\num{1000}$ & 10~days &
		Mixed sampling, discrete features fixed.\\
		\bottomrule
		\end{tabular}
	}
	\caption{Parameters of sampling runs.}
	\label{tbl:sampling-runs}
\end{table}

@@

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{r|lllllll}
		\toprule
		{} & \multicolumn{7}{c}{Discrete feature assignment}\\
		Jobs & BBM & BCM & BMM & BSM & FAM & FCM & FSM \\
		\midrule
		0-99 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
		100-199 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
		200-299 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
		300-399 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
		\bottomrule
		\end{tabular}
	}
	\caption{Selected discrete feature assignments corresponding to slices in run~2.}
	\label{tbl:slices}
\end{table}

@@

@@

\begin{wrapfigure}{r}{0.5\textwidth}
  \vspace{-55pt}
  \begin{center}
    \hspace*{-.3\columnsep}\includegraphics[width=0.58\textwidth]{fig3_allvar.jpg}
    \caption{Semivariograms for MC TBR data with coolant materials: (a) $He$, (b) $H_2O$, (c) $D_2O$}
    \label{fig:var}
  \end{center}
  \vspace{-110pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.4\textwidth}
	\centering
	\vspace{-3ex}
	% TODO: placeholders only, regenerate when time is available
	\begin{subfigure}[b]{\linewidth}
		\centering
		\includegraphics[width=\linewidth]{ae_plot_all_slices_combined}
	\end{subfigure}
	\begin{subfigure}[b]{\linewidth}
		\centering
		\includegraphics[width=\linewidth]{ae_plot_single_slice}
	\end{subfigure}
	\caption{Autoencoder loss in two considered cases of dimensional reduction.}
	\label{fig:autoencoder-loss}
\end{wrapfigure}

>>>>

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{rllll}
		\toprule
		\#	& Sample count & Batch division & Run time (incl. waiting) & Description \\
		\midrule
		0 & \num{100000} & $\num{100}\times\num{1000}$ & 2~days, 23~hours &
		Testing run using older MC TBR version.\\
		1 & \num{500000} & $\num{500}\times\num{1000}$ & 13~days, 20~hours &
		Fully uniform sampling in the entire domain.\\
		2 & \num{400000} & $\num{400}\times\num{1000}$ & 10~days &
		Mixed sampling, discrete features fixed.\\
		\bottomrule
		\end{tabular}
	}
	\caption{Parameters of sampling runs.}
	\label{tbl:sampling-runs}
\end{table}

@@

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{r|lllllll}
		\toprule
		{} & \multicolumn{7}{c}{Discrete feature assignment}\\
		Batches & BBM & BCM & BMM & BSM & FAM & FCM & FSM \\
		\midrule
		0-99 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
		100-199 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
		200-299 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
		300-399 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
		\bottomrule
		\end{tabular}
	}
	\caption{Selected discrete feature assignments corresponding to slices in run~2.}
	\label{tbl:slices}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{run1_400k_tbr_vs_feat}
	% TODO: placeholder only, turn into vector
	\caption{Marginalised dependence of TBR on the choice of continuous
	features.}
  \label{fig:tbr-vs-features}
\end{figure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
  \vspace{-55pt}
  \begin{center}
    \hspace*{-.3\columnsep}\includegraphics[width=0.58\textwidth]{fig3_allvar.jpg}
	\caption{Semivariograms for MC TBR data with coolant materials: (a) \ce{He},
	(b) \ce{H2O}, (c) \ce{D2O}}
    \label{fig:var}
  \end{center}
  \vspace{-110pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.4\textwidth}
	\centering
	\vspace{-3ex}
	% TODO: placeholders only, regenerate when time is available
	\begin{subfigure}[b]{\linewidth}
		\centering
		\includegraphics[width=\linewidth]{ae_all_slices}
	\end{subfigure}
	\begin{subfigure}[b]{\linewidth}
		\centering
		\includegraphics[width=\linewidth]{ae_single_slice}
	\end{subfigure}
	\caption{Autoencoder loss in two considered cases of dimensional reduction.}
	\label{fig:autoencoder-loss}
\end{wrapfigure}
